A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-10-08 paper/paper.tex
paper/sec:eqproperties: polish

\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule. This includes in particular the groupoid properties of equality. Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$. Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd). (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type. In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is functional extensionality, holds by default in extensional type theory.

>>>>

\subsection{Groupoid properties of equality and basic type isomorphisms\label{sec:eqproperties}}
The construction takes benefit of various provable equalities over proofs of equality being definitional by the reflection rule. This includes in particular the groupoid properties of equality. Notably, uniqueness of identity proofs holds in extensional type theory, so that any type is automatically an $\U$. Also, we left implicit in table~\ref{tab:coh} the use of the isomorphism between $u = v$ and $\Sigma (p:u.\hd = v.\hd). (u.\tl = v.\tl)$ for $u$ and $v$ in a $\Sigma$-type. In the same table, we also left implicit the use of the isomorphism between $f = g$ and $\Pi a: A.\, f(a) = g(a)$ for $f$ and $g$ in $\Pi a: A.\, B$, where it should be recalled that the right-to-left map, that is functional extensionality, holds by default in extensional type theory. As a final remark, note, as a consequence of $\eta$-conversion for finite enumerated types, that the requirement of functional extensionality disappears when $\nu$ is finite. However, this is a conversion which Coq does not implement, so, in Coq, the alternative would be to replace $\Pi a: \nu.\, B$ by a ``flat'' iterated product $B(1) \times B(2) \times \ldots \times B(\nu)$.
